Dynein notes

### 2018-05-03 papers/notes/notes.tex
very minor change

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c | c |}
    \hline
    Source & Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    Weihong 2012 GST-dimerized & 134nm/s & 3.5nm? &  & 7.9s & 0.0595s & \\ \hline
    Higuchi 2006 & 800nm/s &  &  &   &   & \\ \hline
    Schroer 2000 native 2mM ATP w/ 210nm beads            & 700nm/s & 3.5nm? & 0.005s & 1s    & 5e-3s & 2.5e-5\\ \hline
    Schroer 2000 native 2mM ATP w/ 210nm beads + dynactin & 700nm/s & 3.5nm? &  & 2.14s &  & 6e-5\\ \hline
    Vale    2006 GST-dimerized 1mM + qdots                & 87 nm/s &  & 0.09s  & 13.8s & &\\ \hline
    Schroer 2000 organic dye-labelled full-length dynein & 120nm/s &  &  &  &  & \\ \hline

>>>>

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c | c |}
    \hline
    Source & Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    Weihong 2012 GST-dimerized & 134nm/s & 3.5nm? &  & 7.9s & 0.0595s & \\ \hline
    Higuchi 2006 & 800nm/s &  &  &   &   & \\ \hline
    Schroer 2000 native 2mM ATP w/ 210nm beads            & 700nm/s & 1.7nm? & 0.0025s & 1s    & 2.5e-3s & 6e-6\\ \hline
    Schroer 2000 native 2mM ATP w/ 210nm beads + dynactin & 700nm/s & 3.5nm? &  & 2.14s &  & 6e-5\\ \hline
    Vale    2006 GST-dimerized 1mM + qdots                & 87 nm/s &  & 0.09s  & 13.8s & &\\ \hline
    Schroer 2000 organic dye-labelled full-length dynein & 120nm/s &  &  &  &  & \\ \hline
